A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-07 main.tex
PYEX

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances of Parikh
automata intersection problems generated by the \Ostrich{} string constraint
solver when solving the \Fudge{pyex benchmarks}. After generating an
initial~\InitialNrBenchmarks{}, we remove~\NrBroken{} misgenerated instances
that did not parse, as well as~\NrTrivial{} instances solved in under five
seconds by baseline. The benchmarks are run on commit~\texttt{\commit}.

@@

In this paper we have introduced a calculus to compute commutating operations on
intersections of regular languages that we call \Calculus{}. We have evaluated
it on \NrBenchmarks{} Parikh automata intersection problems generated \Fudge{by
the Ostrich+} string solver \cite{ostrich} solving \Fudge{standard string
constraint benchmarks} using our Parikh automata solver \Catra{}.

>>>>

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances of Parikh
automata intersection problems generated by the \OstrichPlus{} string constraint
solver when solving the PyEx benchmarks~\cite{pyex}. After generating an
initial~\InitialNrBenchmarks{}, we remove misgenerated instances that did not
parse, as well as~\NrTrivial{} instances solved in under five seconds by
baseline. The benchmarks are run on commit~\texttt{\commit}.

@@

In this paper we have introduced a calculus to compute commutating operations on
intersections of regular languages that we call \Calculus{}. We have evaluated
it on \NrBenchmarks{} Parikh automata intersection problems generated by the
\OstrichPlus{} string solver \cite{ostrich-plus} solving the PyEx benchmark
suite \cite{pyex} using our Parikh automata solver \Catra.
